Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-09-05 papers/paper/ms.tex
update figure stlye

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points.  Kepler-1627 is in the outskirts of the $\delta$\ Lyr
  cluster \citep{bouma_kep1627_2022}, which is centered at $(l,b)
  \approx (66^\circ, 12^\circ)$.
  The Kepler footprint is shown in gray.
  {\it Middle row}: Galactic positions.  The Sun is at $(X, Y, Z) =
  (0, 0, 20.8)$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  galactic longitudinal velocity versus galactic longitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest \citep{schonrich_local_2010}.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 (magenta\added{; smaller circles}).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2'' (lime-green\added{; larger
  circles}).
  The selection method for \replaced{all of the stars}{these groups}
  is described in Section~\ref{subsec:members}.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{f2d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Age-diagnostic diagrams from the stellar groups near
    Kepler-1643, KOI-7368, and KOI-7913.} 
    {\it Top row}: Color--absolute magnitude diagram of candidate
    Cep-Her members, plotted over candidate members of the
    $\delta$~Lyr~cluster ($\approx38$\,Myr;
    \citealt{bouma_kep1627_2022}) and the Gaia EDR3 Catalog of Nearby
    Stars (gray background).  The left and right columns shows stars
    in RSG-5 and CH-2, respectively.  The range of colors is truncated
    to emphasize the pre-main-sequence.  Stars that fall far below the
    cluster sequences are field interlopers.  {\it Bottom row}:
    TESS and ZTF-derived stellar rotation periods, with the Pleiades
    ($\approx 112$\,Myr) and Praesepe ($\approx 650$\,Myr) shown for
    reference \citep{rebull_rotation_2016a,douglas_poking_2017}.  The
    detection efficiency for reliable rotation periods falls off
    beyond $\bpmrpo \gtrsim 2.6$.
	\label{fig:age}
	}
\end{figure*}

@@

For CH-2, 13/19 stars have rotation periods that are obviously faster
than their counterparts in the Pleiades\deleted{ (68\%)}.  4 stars, not included
in the preceding numerator, are M-dwarfs with rotation periods between
10 and 12.5 days.  As previously noted, the age interpretation for
these M-dwarfs is not obvious.  \added{If none are cluster members,
the rotation period detection fraction is 68\%; if all are members, it
is 89\%}.
\replaced{Regardless, the $\approx$15\% false
positive rate for CH-2 determined from the CAMD seems consistent with
our fraction of detected rotation periods; RSG-5 was missing rotation
periods for $\approx$15\% of its candidate members, even though all of
its stars appear photometrically consistent with being on a single
pre-main-sequence locus.}{
This sets an upper bound on the contaminant fraction in our candidate
CH-2 members at about one in three.  The true value may be as low as 
one in six, based on our earlier CAMD analysis.
}

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f6a.pdf}
		}

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f6b.pdf}
		}

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f6c.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Lithium 6708\AA\ and H$\alpha$ equivalent widths for the
    objects of interest compared to young open clusters and field
    stars. } Positive equivalent width means absorption; negative
    equivalent width means emission.  
    {\it Top \& middle}:
    The field stars are KOIs from
    \citet{berger_identifying_2018}.  The ``40-50 Myr'' reference
    stars ({\it left}) are from IC\,2602 \citep{randich_gaiaeso_2018} and
    Tuc-Hor \citep{kraus_stellar_2014}.  The ``112 Myr'' stars
    are from the Pleiades
    \citep{soderblom_evolution_1993,jones_evolution_1996,bouvier_pleiades_lirot_2018}.
    The statistical uncertainties on
    the equivalent widths are shown, or else are
    smaller than the markers.
    {\it Bottom}:
    The H$\alpha$ comparison is against Tuc-Hor
    \citep[$\approx$$40$\,Myr;][]{kraus_stellar_2014}
    \label{fig:lithium}
	}
\end{figure}

@@

		\vspace{-1.27cm}	
		\subfloat{
			\includegraphics[width=0.33\textwidth]{f3d.pdf}
			\includegraphics[width=0.33\textwidth]{f3e.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Raw and processed light curves for the Kepler Objects of
    Interest in Cep-Her.}   
    {\it Top}: 50 day light curve segment from the 3.9 years of Kepler
    data.  The ordinate shows the \texttt{PDCSAP} median-subtracted
    flux in units of parts-per-thousand ($\times 10^{-3}$).  The
    dominant signal is from starspots; planetary transit times
    are indicated \added{with vertical dashed lines }but the individual transits are not visible at this scale.
    {\it Bottom}:
    Phase-folded transits of Kepler-1643, KOI-7913, KOI-7368, and
    Kepler-1627 with stellar variability removed.  The maximum a
    posteriori model is shown with the gray line, and the
    residual after subtracting the transit model is vertically
    displaced.  Windows over 10 hours are shown.  Gray points are
    individual flux measurements; black points are binned to 20 minute
    intervals, and have a representative 1-$\sigma$ error bar in the
    center-right of each panel. 
		\label{fig:planets}
	}
\end{figure*}

>>>>

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points.  Kepler-1627 is in the outskirts of the $\delta$\ Lyr
  cluster \citep{bouma_kep1627_2022}, which is centered at $(l,b)
  \approx (66^\circ, 12^\circ)$.
  The Kepler footprint is shown in gray.
  {\it Middle row}: Galactic positions.  The Sun is at $(X, Y, Z) =
  (0, 0, 20.8)$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  galactic longitudinal velocity versus galactic longitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest \citep{schonrich_local_2010}.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 (magenta\added{; smaller circles}).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2'' (lime-green\added{; larger
  circles}).
  The selection method for \replaced{all of the stars}{these groups}
  is described in Section~\ref{subsec:members}.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{f2d.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Age-diagnostic diagrams from the stellar groups near
    Kepler-1643, KOI-7368, and KOI-7913.} 
    {\it Top row}: Color--absolute magnitude diagram of candidate
    Cep-Her members, plotted over candidate members of the
    $\delta$~Lyr~cluster ($\approx38$\,Myr;
    \citealt{bouma_kep1627_2022}) and the Gaia EDR3 Catalog of Nearby
    Stars (gray background).  The left and right columns shows stars
    in RSG-5 and CH-2, respectively.  The range of colors is truncated
    to emphasize the pre-main-sequence.  Stars that fall far below the
    cluster sequences are field interlopers.  {\it Bottom row}:
    TESS and ZTF-derived stellar rotation periods, with the Pleiades
    ($\approx 112$\,Myr) and Praesepe ($\approx 650$\,Myr) shown for
    reference \citep{rebull_rotation_2016a,douglas_poking_2017}.  The
    detection efficiency for reliable rotation periods falls off
    beyond $\bpmrpo \gtrsim 2.6$.
	\label{fig:age}
	}
\end{figure*}

@@

For CH-2, 13/19 stars have rotation periods that are obviously faster
than their counterparts in the Pleiades\deleted{ (68\%)}.  4 stars, not included
in the preceding numerator, are M-dwarfs with rotation periods between
10 and 12.5 days.  As previously noted, the age interpretation for
these M-dwarfs is not obvious.  \added{If none are cluster members,
the rotation period detection fraction is 68\%; if all are members, it
is 89\%}.
\replaced{Regardless, the $\approx$15\% false
positive rate for CH-2 determined from the CAMD seems consistent with
our fraction of detected rotation periods; RSG-5 was missing rotation
periods for $\approx$15\% of its candidate members, even though all of
its stars appear photometrically consistent with being on a single
pre-main-sequence locus.}{
This sets an upper bound on the contamination fraction in our candidate
CH-2 members at about one in three.  The true value may be as low as 
one in six, based on the earlier CAMD analysis.
}

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f6a.pdf}
		}

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f6b.pdf}
		}

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f6c.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Lithium 6708\AA\ and H$\alpha$ equivalent widths for the
    objects of interest compared to young open clusters and field
    stars. } Positive equivalent width means absorption; negative
    equivalent width means emission.  
    {\it Top \& middle}:
    The field stars are KOIs from
    \citet{berger_identifying_2018}.  The ``40-50 Myr'' reference
    stars ({\it left}) are from IC\,2602 \citep{randich_gaiaeso_2018} and
    Tuc-Hor \citep{kraus_stellar_2014}.  The ``112 Myr'' stars
    are from the Pleiades
    \citep{soderblom_evolution_1993,jones_evolution_1996,bouvier_pleiades_lirot_2018}.
    The statistical uncertainties on
    the equivalent widths are shown, or else are
    smaller than the markers.
    {\it Bottom}:
    The H$\alpha$ comparison is against Tuc-Hor
    \citep[$\approx$$40$\,Myr;][]{kraus_stellar_2014}
    \label{fig:lithium}
	}
\end{figure}

@@

		\vspace{-1.27cm}	
		\subfloat{
			\includegraphics[width=0.33\textwidth]{f3d.pdf}
			\includegraphics[width=0.33\textwidth]{f3e.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Raw and processed light curves for the Kepler Objects of
    Interest in Cep-Her.}   
    {\it Top}: 50 day light curve segment from the 3.9 years of Kepler
    data.  The ordinate shows the \texttt{PDCSAP} median-subtracted
    flux in units of parts-per-thousand ($\times 10^{-3}$).  The
    dominant signal is from starspots; planetary transit times
    are indicated \added{with vertical dashed lines, }but the individual transits are not visible at this scale.
    {\it Bottom}:
    Phase-folded transits of Kepler-1643, KOI-7913, KOI-7368, and
    Kepler-1627 with stellar variability removed.  The maximum a
    posteriori model is shown with the gray line, and the
    residual after subtracting the transit model is vertically
    displaced.  Windows over 10 hours are shown.  Gray points are
    individual flux measurements; black points are binned to 20 minute
    intervals, and have a representative 1-$\sigma$ error bar in the
    center-right of each panel. 
		\label{fig:planets}
	}
\end{figure*}
